\begin{resumo}[Abstract]
 \begin{otherlanguage*}{english}

Given the vast amount and variety of information on the Internet today, it is possible to create system requirements that help users find or use terms according to their preference, reducing the wasting time spent in the environment. In open ecommerce sites, for example, there are hundreds or thousands of products to show users, and this makes it difficult to find the right product as particular to each customer. The present work deals with the development of a real estate recommendation system, which consists of a B2B (Business to Business) type of business. Through a virtual real estate real estate e-commerce website that presents your properties and gets visibility from your prospective clients, using a referral system for consultants who are looking for the most efficient and diminutive ways or who are trying to use whatever their needs are. particular interests to purchase a new property. The main goal would be to assist customers visiting this virtual site in locating their preferred device more efficiently by developing a more robust recommendation system compared to existing systems. Real estate recommendations used as a base are the characteristics of these customers acquired by the recommended system. It will follow a hybrid approach, that is, contemplating two or more research techniques, generating better results for clients using this system. An initial study was carried out through bibliographical research on concepts, approaches and techniques used in application systems in the industrial context to generate a new recommendation system proposed in this work.

   \vspace{\onelineskip}
 
   \noindent 
   \textbf{Key-words}: machine learning. reccomender system. e-commerce. real estate.
 \end{otherlanguage*}
\end{resumo}
